---
output:
  md_document:
    variant: markdown_github
---

# Question 1

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load the necessary packages

rm(list = ls()) 
invisible(gc())
library(pacman)
p_load(rmsfuns, tidyverse, tbl2xts, devtools, PerformanceAnalytics, ggplot2, TTR, RcppRoll, xts, knitr, ggrepel, fmxdat)
list.files("questions/Question1/code", full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

My goal here is to whey up the performance of the AI fund against the Capped SWIX and a selection of ASISA funds. But more than just making a case for it being the best, which is not necessarily the case 100% of the time here, I want to put its performance in perspective of the ASISA more generally.

I Start by simply looking at and transforming the data according to my viewing pleasure and later needs.

```{r}
# Loading the SWIX
# I first remove the un-necessary columns...
# ...And then create a Fund column with just the name 'Benchmark' repeating so i can cbind it later

bm <- read_rds("questions/Question1/data/Capped_SWIX.rds")%>% 
    dplyr::select(-Tickers) %>% 
    arrange(date) %>% 
    mutate(Fund = "Benchmark")

# Loading the AI fund
# Rename columns to match with my 'bm' format
# Again, create a Fund column with just the name 'AI_Fund' repeating so i can cbind it later

ai_fund <- read_rds("questions/Question1/data/AI_Max_Fund.rds")%>% 
    rename(Returns = AI_Fund) %>%
    arrange(date) %>% 
    mutate(Fund = "AI_Fund")

# Loading the ASISA funds
# Remove un-necessary columns

asisa <- read_rds("questions/Question1/data/ASISA_Rets.rds")%>% 
    dplyr::select(-FoF, -Index) %>% 
    arrange(date) 

# Now can just simply rbind() these together and filter the dates to start at in September of 2003
# Simply because it gives a nice 20 year sample :)

data = rbind(bm, ai_fund, asisa) %>% 
    arrange(date) %>% 
    dplyr::filter(date >= ymd(20080131))

```

Now that all of the funds have been put into a single data set, in long format for easy calculations and plotting, I want to calculate the returns. I use cumulative returns to see the overall period gain, and 12 month rolling returns for a more direct comparison.

```{r}
# Calculating the different type of returns

data <- data %>% 
    
    # First calculating cumulative returns
    
    mutate(Returns = coalesce(Returns, 0)) %>% 
    group_by(Fund) %>% 
    mutate(Cum_Ret = cumprod(1 + Returns)) %>% 
    
    # Now calculating rolling returns
    
    mutate(Rolling_Ret = RcppRoll::roll_prod(1 + Returns,
                                             12,
                                             fill = NA,
                                             align = "right") ^ (12 / 12) - 1) %>%  
    group_by(date) %>% 
    filter(any(!is.na(Rolling_Ret))) %>% 
    ungroup() 
```

With the returns calculated, I decide which ASISA funds I am going to make my comparison too. I decide to first calculate how many of these funds actually beat the benchmark in terms of cumulative returns at the end of the period.

```{r}
# Calculating the end of period benchmark cumulative return

bm_cum_ret <- data %>% 
    dplyr::filter(date == max(date)) %>% 
    dplyr::filter(Fund == "Benchmark") %>% 
    pull(Cum_Ret)

# Using the above, I create a dummy for whether a fund beats the benchmark or not and calculate the percentage that do

exceed <- data %>% 
    dplyr::filter(date == max(date)) %>% 
    dplyr::filter(!(Fund %in% c("AI_Fund", "Benchmark"))) %>% 
    mutate(exceed = ifelse(Cum_Ret >= max(bm_cum_ret), 1, 0)) %>% 
    mutate(percent_exceed = sum(exceed) / length(unique(Fund)) * 100) %>% 
    pull(percent_exceed) %>% 
    unique
```

We see here that only 9.4% of funds exceed the benchmark. Sheesh. Based on this I decide to compare the AI fund to the top 5 best performing ASISA funds rather than those that it will definately outperform.

```{r}
# Determining the top 5

best_asisa <- data %>% 
    dplyr::filter(date == max(date)) %>% 
    dplyr::filter(!(Fund %in% c("AI_Fund", "Benchmark"))) %>% 
    mutate(exceed = ifelse(Cum_Ret >= bm_cum_ret, 1, 0)) %>% 
    dplyr::filter(exceed == 1) %>% 
    arrange(desc(Cum_Ret)) %>% 
    head(5) %>% 
    pull(Fund)

# Now filter the ASISA fund to only look at these 5 and our other two measures

data_subset1 <- data %>% 
    dplyr::filter(Fund %in% c(best_asisa, c("AI_Fund", "Benchmark")))
```

Now I plot the cumulative returns of each fund in relation to their improvement from the benchmark. The AI fund being red and the benchmark black

```{r echo=FALSE, message=FALSE, warning=FALSE}
# First calculating the final cumulative difference from the benchmark

diffs <- data_subset1 %>%
    group_by(Fund) %>%
    dplyr::filter(date == max(date)) %>%
    ungroup()

# Getting the max benchmark 

bench_diff <- diffs %>%
    dplyr::filter(Fund == "Benchmark") %>%
    pull(Cum_Ret)

# Calculating the gain of the other funds from this max

diffs <- diffs %>%
    dplyr::filter(!Fund == "Benchmark") %>%
    mutate(final_diff = Cum_Ret / bench_diff * 100 - 100) %>%
    dplyr::filter(!Fund == "Benchmark")

# Getting the funds not including the benchmark

funds <- data_subset1 %>%
    filter(!Fund == "Benchmark")

# Getting only the benchmark

bench <- data_subset1 %>%
    filter(Fund == "Benchmark")

ggplot() +
    geom_line(data = bench,
              aes(x = date,
                  y = Cum_Ret),
              color = "black",
              size = 1.2) +
    geom_line(data = funds %>% dplyr::filter(!Fund == "AI_Fund"),
              alpha = 0.7,
              size = 0.8,
              aes(x = date,
                  y = Cum_Ret,
                  color = Fund)) +
    geom_line(data = funds %>% dplyr::filter(Fund == "AI_Fund"),
              alpha = 0.7,
              size = 1.2,
              color = "red",
              aes(x = date,
                  y = Cum_Ret,
                  color = Fund)) +
    geom_label_repel(data = diffs,
                     aes(x = date,
                         y = Cum_Ret,
                         label = paste0(round(final_diff, 1), "%")),
                     size = ggpts(10),
                     alpha = 1,
                     color = "black",
                     fontface = "bold",
                     nudge_x = 220) +
    labs(title = "Cumulative returns of top ASISA funds",
         subtitle = "Base Return: Benchmark",
         y = "Cumulative Return",
         x = "Date")
```

Now I want to compare the 5 funds once they have had a 300 basis point fee applied to them. Here I follow the same logic as above, however, first I need to apply the fee to the original cumulative returns

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Basis points to %

fee_rate <- 300 / 10000

# Annual rate compounded monthly

monthly_fee_rate <- (1 + fee_rate) ^ (1/12) - 1

# Apply monthly fee rate cumulatively using compound interest

asisa_fee1 <- data_subset1 %>%
    arrange(date) %>%
    dplyr::filter(Fund %in% best_asisa) %>%
    group_by(Fund) %>%
    mutate(Fee = Returns - monthly_fee_rate) %>%
    mutate(Fee_Cum = cumprod(1 + Fee))

# Now recalculate the percentage gain over the benchmark with the new cumulative returns for the 5 funds, and the same max as before

diffs2 <- asisa_fee1 %>%
    group_by(Fund) %>%
    filter(date == max(date)) %>%
    ungroup()%>%
    dplyr::filter(!Fund == "Benchmark") %>%
    mutate(final_diff = Fee_Cum / bench_diff * 100 - 100) %>%
    filter(!Fund == "Benchmark")

funds2 <- asisa_fee1 %>%
    filter(!Fund == "Benchmark")

ggplot() +
    geom_line(data = bench,
              aes(x = date,
                  y = Cum_Ret),
              color = "black",
              size = 1.2) +
    geom_line(data = funds2 %>% dplyr::filter(!Fund == "AI_Fund"),
              alpha = 0.7,
              size = 0.8,
              aes(x = date,
                  y = Fee_Cum,
                  color = Fund)) +
    geom_line(data = funds %>% dplyr::filter(Fund == "AI_Fund"),
              alpha = 0.7,
              size = 1.2,
              color = "red",
              aes(x = date,
                  y = Cum_Ret,
                  color = Fund)) +
    geom_label_repel(data = diffs2,
                     aes(x = date,
                         y = Fee_Cum,
                         label = paste0(round(final_diff, 1), "%")),
                     size = ggpts(10),
                     alpha = 1,
                     color = "black",
                     fontface = "bold",
                     nudge_x = 220) +
    labs(title = "Cumulative returns of top ASISA funds",
         subtitle = "Base Return: Benchmark",
         y = "Cumulative Return",
         x = "Date")
```

With the fee applied, the difference between these funds and the AI fund is far less drastic. Now it is competing right up there with the big dogs. However, it is also useful to look at those rolling returns we calculated.

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot() +
    geom_line(data = data_subset1 %>% dplyr::filter(Fund %in% best_asisa),
              aes(x = date,
                  y = Rolling_Ret,
                  color = Fund),
              size = 0.7,
              alpha = 0.5) +
    geom_line(data = data_subset1 %>% dplyr::filter(Fund %in% c("Benchmark")),
              aes(x = date,
                  y = Rolling_Ret),
              color = "black", 
              linetype = "dashed",
              size = 0.8) +
    geom_line(data = data_subset1 %>% dplyr::filter(Fund %in% c("AI_Fund")),
              aes(x = date,
                  y = Rolling_Ret),
              size = 0.8,
              color = "red") +
    labs(x = "Date",
         y = "Rolling Returns") +
    theme_bw()   
```

Then I also want to see how often each fund is under or over performing compared to the benchmark

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Creating a new character variable that defines the state of the fund relative to the benchmark

strat1 <- data_subset1 %>% 
    dplyr::select(date, Fund, Rolling_Ret) %>% 
    pivot_wider(names_from = Fund,
                values_from = Rolling_Ret) %>% 
    pivot_longer(cols = c(-date, -Benchmark),
                 names_to = "Fund", 
                 values_to = "Returns") %>% 
    group_by(Fund) %>% 
    mutate(Performance = case_when(Returns > Benchmark ~ "Outperforming",
                                   Returns < Benchmark ~ "Underperforming",
                                   TRUE ~ "No Data"))

ggplot(strat1, aes(x = Fund, fill = Performance)) +
  geom_bar() +
  labs(title = "Performance Comparison of Funds vs Benchmark",
       x = "Performance Category",
       y = "Number of Observations") + 
    theme_bw()
```
However, the above is a best case scenario, I also wanted to get a random selection of the funds to should what an average case may look like. When we do this, we see a very different story, with the AI fund coming out on top.

The seed was randomly typed out until I got a selection with a nice amount of available data

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Randomly select 5 funds

set.seed(98765)

data_subset2 <- data %>% 
    dplyr::filter(Fund %in% c(sample(unique(asisa$Fund), 5), c("AI_Fund", "Benchmark")))

# Do the same plot as above

strat2 <- data_subset2 %>% 
    dplyr::select(date, Fund, Rolling_Ret) %>% 
    pivot_wider(names_from = Fund,
                values_from = Rolling_Ret) %>% 
    pivot_longer(cols = c(-date, -Benchmark),
                 names_to = "Fund", 
                 values_to = "Returns") %>% 
    group_by(Fund) %>% 
    mutate(Performance = case_when(Returns > Benchmark ~ "Outperforming",
                                   Returns < Benchmark ~ "Underperforming",
                                   TRUE ~ "No Data"))

ggplot(strat2, aes(x = Fund, fill = Performance)) +
  geom_bar() +
  labs(title = "Performance Comparison of Funds vs Benchmark",
       x = "Performance Category",
       y = "Number of Observations") +
    theme_bw()
```

# Question 2

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load the necessary packages

rm(list = ls()) 
invisible(gc())
library(pacman)
p_load(rmsfuns, tidyverse, tbl2xts, devtools, PerformanceAnalytics, ggplot2, TTR, RcppRoll, xts, knitr, ggrepel, fmxdat, gt)
list.files("questions/Question2/code", full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

Here I want to determine whether hedging a portfolio is a good strategy in the long-term or not by replicating the study asking the same question. I start by simply looking at the data and making my desired transformations.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Loading the data
# Flooring the date so that it will be the same as the ZAR data to join later

indices <- read_rds("questions/Question2/data/Cncy_Hedge_Assets.rds") %>% 
    mutate(date = floor_date(date, "month"))

# Reading the monthly value for the ZAR to the USD
# Calculating the currency returns

zar <- read_rds("questions/Question2/data/Monthly_zar.rds") %>% 
    mutate(fx_change = log(value) - log(lag(value))) %>% 
    dplyr::select(-Tickers) %>% 
    mutate(date = floor_date(date, "month"))
```

First I want to replicate the scatter plot showing when hedging has a good or bad outcome. To do this I need to construct a simple 2 variable USD index of just MSCI_ACWI and Bbg_Agg. So I separate these from my indices data frame and apply a 60 equity and 40 bond split respectively. I do no re-balancing here. Just simple aggregation. The plot is then simply the portfolio on the y-axis and the ZAR returns on the x-axis

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Impact of ZAR Hedging", fig1}
# Constructing the global 60 - 40 USD portfolio...
# And join it to the ZAR currency returns

us_hedged_port <- indices %>% 
    dplyr::select(date, MSCI_ACWI, Bbg_Agg) %>% 
    pivot_longer(cols = -date,
                 names_to = "Index",
                 values_to = "Returns") %>% 
    mutate(Weights = ifelse(Index == "MSCI_ACWI", 0.6, 0.4)) %>% 
    group_by(date) %>% 
    mutate(portfolio = sum(Weights * Returns)) %>% 
    dplyr::select(date, portfolio) %>% 
    unique() %>% 
    inner_join(zar, by = "date")

# And recreating the plot from the study

fmxdat::finplot(us_hedged_port %>% 
    ggplot(aes(x = fx_change,
               y = portfolio))+
    geom_rect(aes(xmin = -Inf, xmax = 0, ymin = 0, ymax = Inf), fill = "yellow4", alpha = 0.002) +  
    geom_rect(aes(xmin = 0, xmax = Inf, ymin = 0, ymax = Inf), fill = "green3", alpha = 0.002) +  
    geom_rect(aes(xmin = -Inf, xmax = 0, ymin = -Inf, ymax = 0), fill = "red", alpha = 0.002) +  
    geom_rect(aes(xmin = 0, xmax = Inf, ymin = -Inf, ymax = 0), fill = "yellow", alpha = 0.002) +  
    geom_point(color = "darkblue",
               alpha = 0.5) +
    geom_smooth(method = "lm",
                color = "darkgrey", 
                se = F) +
    geom_hline(yintercept = 0, 
               color = "black", 
               linetype = "dashed", 
               size = 0.5) +
    geom_vline(xintercept = 0, 
               color = "black", 
               linetype = "dotted", 
               size = 0.5) +
    labs(x = "60-40 Global (USD Returns",
         y = "USD-ZAR Returns"))
```

Lekka, got what I wanted. This scatter plot can now be used to interpret the effects of ZAR hedging. Now I can move on to calculating the local global split portfolios. 70 local 30 global with the same equity bond split above. The weights are determine by multiplying the respective percentages for each variable together. This is then re-balanced quarterly.

This needs to be done for both a hedged and an unhedged portfolio. The unhedged portfolio needs to have the USD assets adjusted for ZAR exposure by adding the ZAR returns to it. The hedged leaves the USD assets as is.

All of this is taken into account by the estimatePORT function that calculates the portfolio for you.

```{r message=FALSE, warning=FALSE}
# Estimate the weights of the index according to specifications

weights <- data.frame(Index = colnames(indices)[sapply(indices, is.numeric)],
                      Weights = c(0.6 * 0.3, 0.4 * 0.3, 0.6 * 0.7, 0.4 * 0.7))

# Estimating an hedged index
# Hedged indices are those that do not account for rand exposure, so we do nothing to these indices

hedged_indices <- indices 

hedged_port <- estimatePORT(data = hedged_indices,
                            size = 1000,
                            months = c(3, 6, 9, 12),
                            weights = weights)

# Now estimating as un-hedged portfolio
# Need to control USD returns for currency effects, do this by adding the change in the rand to the USD indices

unhedged_indices <- indices %>% 
    inner_join(zar, by = "date") %>% 
    mutate(MSCI_ACWI = MSCI_ACWI + fx_change,
           Bbg_Agg = Bbg_Agg + fx_change) %>%
    dplyr::select(-fx_change, -value) 

unhedged_port <- estimatePORT(data = unhedged_indices,
                              size = 1000,
                              months = c(3, 6, 9, 12),
                              weights = weights)
```

Then we need to calculate the annualized returns and standard deviations for each portfolio, including the original USD asset portfolio from before. This is done with the PerformanceAnalytics package. this is then all put nicely into a table for viewing.

This requires the data to be in xts format.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Annualized returns
# The USD portfolio

us_hedged_annual_ret <- us_hedged_port %>% 
    dplyr::select(date, portfolio) %>% 
    tbl_xts() %>% 
    Return.annualized(R = ., 
                      scale = 12) %>% 
    data.frame()

# The local global hedged portfolio

hedged_annual_ret <- hedged_port$returns %>% 
    xts_tbl() %>% 
    filter(date >= ymd(20041201) & date <= ymd(20221201)) %>% 
    tbl_xts() %>% 
    Return.annualized(R = ., 
                      scale = 12) %>% 
    data.frame()

# The local global unhedged portfolio

unhedged_annual_ret <- unhedged_port$returns %>% 
    xts_tbl() %>% 
    filter(date >= ymd(20041201) & date <= ymd(20221201)) %>% 
    tbl_xts() %>% 
    Return.annualized(R = ., 
                      scale = 12) %>% 
    data.frame()

# Annualized SD
# The USD portfolio

hedged_annual_sd <- hedged_port$returns %>% 
    sd.annualized(x = ., 
                      scale = 12)

# The local global hedged portfolio

unhedged_annual_sd <- unhedged_port$returns %>% 
    sd.annualized(x = ., 
                      scale = 12)

# The local global unhedged portfolio

us_hedged_annual_sd <- us_hedged_port %>% 
    dplyr::select(date, portfolio) %>% 
    filter(date >= ymd(20041201) & date <= ymd(20221201)) %>% 
    tbl_xts() %>% 
    sd.annualized(x = ., 
                  scale = 12)

# Putting all into a table

port_comp_table <- data.frame(Fund = c("Global (USD Returns: Hedged","Global + Local (Hedged)", "Global + Local (Unhedged"),
                        "Returns Ann." = c(us_hedged_annual_ret$portfolio, hedged_annual_ret$portfolio.returns, unhedged_annual_ret$portfolio.returns),
                        "Std Ann." = c(us_hedged_annual_sd, hedged_annual_sd, unhedged_annual_sd))

port_comp_table %>% 
    gt(caption = "Portfolio Performance")
```

This is not an exact match but a decent replication of the study. I further decide to plot some downside risk estimates and the cumulative returns of the hedged and unhedged portfolios again using performance analytics to further home in on the points above. 

Unhedged is better on all accounts over the long term.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# First I join the two portfolio returns together into a single xts object for comparative plotting

portfolios <- left_join(hedged_port$returns %>% xts_tbl() %>% rename("Hedged" = portfolio.returns),
                        unhedged_port$returns %>% xts_tbl() %>% rename("Unhedged" = portfolio.returns),
                        by = "date") %>% 
    filter(date >= ymd(20041201) & date <= ymd(20221201)) %>% 
    tbl_xts()

# Making the downside risk table with these indices
    
downside_table <- PerformanceAnalytics::table.DownsideRisk(R = portfolios,
                                             ci = 0.95,
                                             Rf = 0, 
                                             MAR = 0) %>% data.frame() %>% 
    rownames_to_column(var = "Estimate") 

downside_table[c(1,5,7,8:11),] %>% 
    gt(caption = "Downside Risks")

# Cumulative returns with these indices

chart.CumReturns(R = portfolios,
                 width = 12, 
                 main = "",
                 legend.loc = "topleft",
                 colorset = c("steelblue", "orange"))
    
```

# Question 3

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Necessary packages

rm(list = ls()) 
invisible(gc())
library(pacman)
p_load(rmsfuns, tidyverse, tbl2xts, devtools, PerformanceAnalytics, ggplot2, TTR, RcppRoll, xts, gt, knitr, ggpubr)
list.files('questions/Question3/code', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

The goal here is to compare the ALSI and SWIX methodologies by looking at sectoral performance and varying index sizes and then within this context evaluating the impact of various capping levels and whether they are necessary. 

The instruction here was to use Texeveir, however, I could not get it to knit. Maybe since I switched to windows 11? It used to work before that but I cant be sure thats the reason. I just used Quarto instead. Apologies.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Loading the ALSI data and getting a look
# Filtering the data to start in 2013 as it when there is the most available data in small caps

data <- read_rds("data/ALSI.rds") %>% 
    dplyr::filter(date > ymd(20131231))
```

Here I was a bit confused by what the J203 and J403 were communicating but summing them together revealed they are the weights for each ticker as they sum to one for each day

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Weights summed to 1

data %>% group_by(date) %>% summarise(sum(J203))
data %>% group_by(date) %>% summarise(sum(J403))
```

Calculated the indices from this using simple aggregation with the weight for each stock and its returns for each respective day.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# First looking at the indices

indices <- data %>% 
    group_by(date) %>% 
    mutate(ALSI = sum(J203 * Return),
           SWIX = sum(J403 * Return)) %>% 
    dplyr::select(date, ALSI, SWIX) %>% 
    unique() %>% 
    arrange(date)
```

Now I decide to evaluate the performance of each index by plotting the cumulative returns and 12 month rolling standard deviation using PerformanceAnalytics

```{r echo=FALSE, message=FALSE, warning=FALSE}
chart.RollingPerformance(R = indices %>% tbl_xts(),
                         FUN = "sd",
                         width = 120, 
                         main = "Rolling 120 day Standard Deviation", 
                         legend.loc = "bottomleft",
                         colorset = c("steelblue", "orange"))

chart.CumReturns(R = indices%>% tbl_xts(),
                 main = "Portfolios cumulative returns", 
                 legend.loc = "topleft",
                 colorset = c("steelblue", "orange"))

```
The relationship of the indices reverses after the covid period. I am going to investigate this through their sectoral compositions. I do this by Summing the weights for each stock belonging to a given sector together and seeing how this changes over time.

```{r echo=FALSE, message=FALSE, warning=FALSE}
exposure <- data %>% 
    group_by(date, Sector) %>% 
    mutate(ALSI = sum(J203),
           SWIX = sum(J403)) %>% 
    ungroup() %>% 
    dplyr::select(date, Sector, ALSI, SWIX) %>% 
    unique() %>% 
    arrange(Sector)

ggarrange(ggplot() + geom_area(data = exposure, aes(x = date, y = ALSI, fill = Sector), alpha = 0.7) + labs(x = "ALSI", y = "") + theme_bw(), 
          ggplot() + geom_area(data = exposure, aes(x = date, y = SWIX, fill = Sector), alpha = 0.7) + labs(x = "SWIX", y = "") +theme_bw(),
          nrow = 1, ncol = 2,
          common.legend = T,
          legend = "bottom")
```
I also want to see the sectoral composition of each type of stock cap. To better understand the above

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Stocks by size and sector

data %>% 
    dplyr::select(Tickers, Index_Name, Sector) %>% 
    unique() %>%  
    mutate(Index_Name = ifelse(is.na(Index_Name), "Not Specified", Index_Name)) %>% 
    ggplot() +
    geom_bar(aes(x = Index_Name, 
                 fill = Sector)) +
    labs(title = "Stocks by Size and Sector",
       x = "Index Size",
       y = "Number of Observations") + 
    theme_bw()
```
There is a strong influence of resource based stocks after the covid period. Unfortunately, there is a lot of unclassified cap sizes. I then decide to also look at the average cumulative returns and 120 day rolling standard deviation of each cap to assess their performance. 

Small caps seem to perform the best, with the highest returns and lowest volatility. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
data %>% 
    dplyr::select(date, Return, Index_Name) %>% 
    dplyr::filter(!is.na(Index_Name)) %>%
    group_by(date, Index_Name) %>% 
    mutate(Perf = mean(Return)) %>% 
    dplyr::select(-Return) %>% 
    unique() %>% 
    pivot_wider(names_from = Index_Name,
                values_from = Perf) %>% 
    tbl_xts() %>% 
    chart.CumReturns(R = .,
                 main = "Index size mean cumulative returns", 
                 legend.loc = "topleft")
data %>% 
    dplyr::select(date, Return, Index_Name) %>% 
    dplyr::filter(!is.na(Index_Name)) %>%
    group_by(date, Index_Name) %>% 
    mutate(Perf = mean(Return)) %>% 
    dplyr::select(-Return) %>% 
    unique() %>% 
    pivot_wider(names_from = Index_Name,
                values_from = Perf) %>% 
    tbl_xts() %>% 
    chart.RollingPerformance(R = .,
                         FUN = "sd",
                         width = 120, 
                         main = "Rolling 120 day Standard Deviation", 
                         legend.loc = "topleft")

```

Now lets cap our indices. First the requires us to know the re balance dates which we filter out of the days data, and then use to filter the main data. One we have the data for the indices on the days they are re balanced, we separate it into seperate data for the ALSI and SWIX to feed into our function in the next step.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Getting the re balance data by filtering the original data according to the re balance days

days <- read_rds("questions/Question3/data/Rebalance_days.rds") %>% 
    dplyr::filter(Date_Type == "Reb Trade Day") %>% 
    pull(date)

rebalance <- data %>% 
    dplyr::filter(date %in% days) %>%
    mutate(rebalance_time = format(date, "%Y%B")) %>% 
    dplyr::select(-Return, -Sector, -Index_Name)

# Separating the re-balance data
# The renaming is done simply to meet the requirements of the function I wrote

ALSI_Reb <- rebalance %>%  
    rename(tickers = Tickers,
           weight = J203) %>% 
    dplyr::select(-J403)

SWIX_Reb <- rebalance %>%  
    rename(tickers = Tickers,
           weight = J403) %>% 
    dplyr::select(-J203)

# Lastly, we need the returns data to actually re balance
# Again, renaming is done simply to meet the requirements of my function

returns <- data %>% 
    dplyr::select(date, Return, Tickers) %>% 
    rename(return = Return,
           tickers = Tickers)
```

Now with our three inputs, we can cap the indices by feeding them into my indexCAP function. I do this four times, a 5% and a 10% cap for each index.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# ALSI caps

ALSI_Cap1 <- indexCAP(data = returns,
                  rebalance = ALSI_Reb,
                  cap = 0.05)
colnames(ALSI_Cap1)[2] <- "ALSI 5% Cap"
                  
ALSI_Cap2 <- indexCAP(data = returns,
                  rebalance = ALSI_Reb,
                  cap = 0.1)
colnames(ALSI_Cap2)[2] <- "ALSI 10% Cap"

# SWIX caps

SWIX_Cap1 <- indexCAP(data = returns,
                  rebalance = SWIX_Reb,
                  cap = 0.05)
colnames(SWIX_Cap1)[2] <- "SWIX 5% Cap"
                  
SWIX_Cap2 <- indexCAP(data = returns,
                  rebalance = SWIX_Reb,
                  cap = 0.1)
colnames(SWIX_Cap2)[2] <- "SWIX 10% Cap"
```

With the capped indices I create a table of all versions of the index, the four capped ones, and the original two. So three versions of each index. with this I use performance analytics to estimate the cumulative returns for 6 indices, only comparing each version of the ALSI to itself and each version of the SWIX to itself. There is no cross index comparison of the caps as I wouldn't know how to interpret it. I also further estimate the downside risks.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Creating the index data frame

capped_indices <- ALSI_Cap1 %>% 
    inner_join(ALSI_Cap2, by = "date") %>% 
    inner_join(SWIX_Cap1, by = "date") %>% 
    inner_join(SWIX_Cap2, by = "date") %>% 
    inner_join(indices, by = "date") %>% 
    tbl_xts()

# Cumulative returns plots

chart.CumReturns(R = capped_indices[, c(1, 2, 5)],
                 main = "ALSI cumulative returns", 
                 legend.loc = "topleft")

chart.CumReturns(R = capped_indices[, c(3, 4, 6)],
                 main = "SWIX cumulative returns", 
                 legend.loc = "topleft")

# Downside risks table

PerformanceAnalytics::table.DownsideRisk(R = capped_indices,
                                         ci = 0.95,
                                         scale = 12)%>% 
    rownames_to_column(var = "Estimates") %>% 
    gt(caption = "Downside Risks")
```

The ALSI benefits from a 10% cap, but the SWIX does not benefit from either the 5% or 10% caps. However, the downside risks do not seem to indicate much benefit.

# Question 4

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Necessary packages

rm(list = ls()) 
invisible(gc())
library(pacman)
p_load(rmsfuns, tidyverse, tbl2xts, devtools, PerformanceAnalytics, ggplot2, TTR, RcppRoll, xts, gt, knitr, ggpubr)
list.files('questions/Question4/code', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

The goal here is basically to figure out what drives the behavior of a snake oil fun, comparing it to a benchmark strategy, in order to establish some quantitative information that can be used to motivate its use.

Start by loading and viewing the data

```{r echo=FALSE, message=FALSE, warning=FALSE}
portholds <- read_rds("questions/Question4/data/Fund_Holds.rds")
portrets <- read_rds("questions/Question4/data/Fund_Rets.rds")
bmholds <- read_rds("questions/Question4/data/BM_Holds.rds")
bmrets <- read_rds("questions/Question4/data/BM_Rets.rds")
```

First I want to look at just the portfolios so I join them together so that they can be easily plotted.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Joining the two funds by their date columns and removing un-necessary columns
# Also converting to xts to be used in performance analytics

portfolios <- inner_join(portrets, bmrets, by = "date") %>% 
    dplyr::select(-Portolio) %>% 
    rename(SO = Returns) %>% 
    tbl_xts()
```

With this we can now estimate a variety of performance measures. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Downside risks

plot(PerformanceAnalytics::table.DownsideRisk(R = portfolios,
                                         ci = 0.95,
                                         scale = 12)%>% 
    rownames_to_column(var = "Estimates") %>% 
    gt(caption = "Downside Risks"))

# Single Factor Asset-Pricing Model Summary

plot(PerformanceAnalytics::table.SFM(Ra = portfolios$SO,
                                Rb = portfolios$BM, 
                                scale = 12,
                                Rf = 0) %>% 
    rownames_to_column(var = "Estimates") %>% 
    gt(caption = "Statistics and STylised Facts"))

# Cumulative returns

PerformanceAnalytics::chart.CumReturns(R = portfolios,
                                       geometric = T,
                                       main = "Cumulative Returns",
                                       legend.loc="bottomright",
                                       colorset = c("steelblue", "orange"),
                                       lwd = 1.5)

# 12-month rolling returns

chart.RollingPerformance(R = portfolios, 
                         width = 12,
                         main="Rolling 12-Month Returns", 
                         legend.loc="bottomleft",
                         colorset = c("steelblue", "orange"),
                         lwd = 1.5)

```
Compared to the benchmark (BM), the snake oil fund (SO) bears consistent similarity across the sample period. However, it mostly falls short of the benchmark on a rolling basis and exhibits slightly worse cumulative returns

The moderate tracking error, and negative information ratio and active premium seem to back this up. In contrast, the Alpha indicates that the snake oil fund outperformed the benchmark after taking risk into account. The Beta further suggests a lower volatility compared to the benchmark.

The snake oil fund exhibits smaller maximum draw downs, as well as smaller modified value at risk and expected shortfall estimates. In other words, the snake oil fund carries less risk. 

```{r}
# Scatter plot

PerformanceAnalytics::chart.Scatter(y = portfolios$SO,
                                    x = portfolios$BM,
                                    main = "Scatter: Snake Oil Funds & Capped SWIX",
                                    ylab = "Snake Oil", 
                                    xlab = "Capped SWIX",
                                    col = "black", 
                                    symbolset = 16)

# 12-month rolling standard deviation

chart.RollingPerformance(R = portfolios,
                         FUN = "sd",
                         width = 12, 
                         main="Rolling 12-Month Standard Deviation", 
                         legend.loc="bottomleft",
                         colorset = c("steelblue", "orange"),
                         lwd = 1.5)

```

Comparing the 12-month rolling volatility, the snake oil fund exhibits much lower volatility in the midst of the pandemic. This suggests an aversion to high levels of risk. 
The scatter plot of returns seems to confirm this. the capped SWIX has a fatter left tail. In other words, the fund experiences smaller relative negative returns than the benchmark during certain periods. Thus, it would seem the fund performs better in positive market conditions, which 2019 to 2024 are not. This is not a proper evaluation of a long-only fund. 

Lastly I want to look at the sectoral composition of the snake oil fund. I wanted to compare it to the SWIX but there were no weights for it and I couldn't figure out a solution for that, so I just look at it in isolation. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# First extracting each unique stock in the snake oil fund

tickers <- portholds %>% dplyr::select(Tickers) %>% unique() %>% pull(Tickers)

# I then want to determine which sector each is from using the Sector column in the benchmark 'bmholds' data
# Using the unique stocks in 'tickers' I filter the benchmark data
# However, there is a duplicate, MNP which as a version for both resources and industrial
# I keep the resources version

so_holds <- bmholds %>% 
    dplyr::select(-date, -name, -Portfolio) %>% 
    unique() %>% 
    dplyr::filter(Tickers %in% tickers) %>% 
    mutate(Dup = duplicated(Tickers)) %>% 
    dplyr::filter(!Dup == T) %>% 
    dplyr::select(-Dup)

# Now with the Stock names and their relative sectors, I can estimate the weights for each sector by summing them together
# Convert to xts to pass to performance analytics

sector_weights <- portholds %>% 
    inner_join(so_holds, by = "Tickers") %>% 
    group_by(date, Sector) %>% 
    mutate(Sector_W = sum(Weight)) %>% 
    dplyr::select(date, Sector, Sector_W) %>% 
    unique() %>% 
    pivot_wider(names_from = Sector,
                values_from = Sector_W) %>% 
    tbl_xts()

# Now using these sector weights to make a stacked bar chart

PerformanceAnalytics::chart.StackedBar(w = sector_weights,
                                       space = 0)
```

As I thought, resources jumped in 2020 as covid hit. Even if I am wrong to choose the resources MNP, removing it from the resource weights would do much to change this chart. 

The fund pushes against risk during crisis periods, and hence in this sample period has performed worse that the benchmark. 

# Question 5 

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Necessary packages

rm(list = ls()) 
invisible(gc())
library(pacman)
p_load(rmsfuns, tidyverse, tbl2xts, devtools, PerformanceAnalytics, ggplot2, TTR, RcppRoll, xts, gt, knitr, ggpubr)
list.files('questions/Question5/code', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))

cncy <- read_rds("questions/Question5/data/currencies.rds")
cncy_carry <- read_rds("questions/Question5/data/cncy_Carry.rds")
cncy_value <- read_rds("questions/Question5/data/cncy_value.rds")
cncyiv <- read_rds("questions/Question5/data/cncyIV.rds")
bbdxy <- read_rds("questions/Question5/data/bbdxy.rds")
```

Here I want to determine whether the ZAR has been one of the most volatile currencies over the last few years. After loading the data and inspecting it, there are many currencies with missing values and different ranges of availability. 

I decide to select 5 currencies to compare, the Euro area, the United Kingdom, India, Japan, Mexico, six with the ZAR included. That is 3 emerging market currencies and 3 G10 currencies. 

I also decide to start the sample at Jan 2000 so that all selected currencies have a complete amount of data.

Once the currencies are selected I plot their prices relative to the dollar over time and calculate the log returns for each. I plot the distributions of the returns as well to determine whether they should be cleaned or not.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Look at 3 emerging market currencies, and 3 G10 currencies

countries <- c("SouthAfrica", "Mexico", "India","UK", "Japan", "EU")

# Calculate the currency returns (dlog)

fx_change <- cncy %>% 
    mutate(Name = gsub("_Cncy", "", Name),
           Name = gsub("_Inv", "", Name)) %>% 
    dplyr::filter(Name %in% countries) %>% 
    group_by(Name) %>% 
    mutate(Return = log(Price) - log(lag(Price)),
           Scaled_Price = Price - mean(Price, na.rm = T)) %>% 
    dplyr::filter(date >= ymd(20000101)) %>% 
    ungroup() 

fmxdat::finplot(fx_change%>% 
                    ggplot() +
                    aes(x = date,
                        y = Price,
                        color = Name) +
                    geom_line(alpha = 0.5) +
                    facet_wrap(~ Name,
                               scales = "free_y") +
                    labs(x = "Price",
                         y = "Date") +guides(alpha = "none")) +
    theme_bw() +
    theme(legend.position = "none") 

fmxdat::finplot(fx_change %>% 
                    ggplot() +
                    aes(x = Return,
                        fill = Name) +
                    geom_histogram(alpha = 0.5) +
                    facet_wrap(facets = ~ Name,
                               scales = "free_y") + 
                    guides(fill = "none", alpha = "none")) +
    theme_bw() +
    theme(legend.position = "none")

```

All three emerging market currencies exhibit a trend of depreciation overtime. However, this trend is also present in one of the G10 currencies, the UK’s currency. 

Furthermore, we see that all currencies have a clumping together of returns in the positive tail which might bias model estimates. Need to clean returns. I do this using performance analytics.

```{r}
# Cleaning the returns
# Needs to be in xts format for performance analytics

cleaned_fx_xts <- fx_change %>% 
    tbl_xts(.,
            cols_to_xts = "Return",
            spread_by = "Name") %>% 
    PerformanceAnalytics::Return.clean(.,
                                       method = "boudt",
                                       alpha = 0.01) 

# Also do a non-xts version for ggploting

cleaned_fx <- cleaned_fx_xts %>% 
    xts_tbl() %>% 
    pivot_longer(cols = -date,
                 names_to = "Currency",
                 values_to = "Return") %>% 
    group_by(Currency) %>% 
    mutate(Return_Sqr = Return ^ 2,
           Return_Abs = abs(Return)) %>% 
    ungroup()
```

I then plot these cleaned returns, their square, and their absolute value

```{r}
# Cleaned returns

fmxdat::finplot(cleaned_fx %>% 
    ggplot() +
    aes(x = date,
        y = Return,
        color = Currency) +
    geom_line(alpha = 0.5) +
    facet_wrap(facets = ~ Currency,
               scales = "free") + 
    ggtitle("Currency returns relative to the USD") +
    guides(alpha = "none"),
                y.pct = T, 
                y.pct_acc = 1) +
    theme_bw()

# Squared cleaned returns

fmxdat::finplot(cleaned_fx %>% 
    ggplot() +
    aes(x = date,
        y = Return_Sqr,
        color = Currency) +
    geom_line(alpha = 0.5) +
    facet_wrap(facets = ~ Currency,
               scales = "free") + 
    ggtitle("Currency returns squared relative to the USD") +
    guides(alpha = "none")) +
    theme_bw()

# Absolute cleaned returns

fmxdat::finplot(cleaned_fx %>% 
    ggplot() +
    aes(x = date,
        y = Return_Abs,
        color = Currency) +
    geom_line(alpha = 0.5) +
    facet_wrap(facets = ~ Currency,
               scales = "free") + 
    ggtitle("Currency returns absolute relative to the USD") +
    guides(alpha = "none")) +
    theme_bw()
```

There is first order and second order persistence here. Will need to deal with this with a GARCH model.

To determine the most optimal type of GARCH to use, I fit multiple GARCH models to just the ZAR and assess via AIC which is best. I built a function, bestGARCH, to do this automatically. In this case a gjrGARCH has been selected as the best by all metrics. 

```{r}
sa_garch <- bestGARCH(data = cleaned_fx_xts$SouthAfrica,
                      comp = c("sGARCH","gjrGARCH","eGARCH","apARCH"),
                      garchOrder = c(1, 1), 
                      armaOrder = c(1, 0),
                      fit = "Akaike")
sa_garch$Criteria
plot(sa_garch$gjrGARCH, which = 3)
```

Now I use a multivariate GARCH model, a Go-GARCH, to apply a gjrGARCH to each series. I do this with a function I wrote, estimateGOGARCH.

```{r message=FALSE, warning=FALSE}
# Feed the cleaned xts returns and specify the type of GARCH

gogarch <- estimateGOGARCH(data = cleaned_fx_xts,
                           type = "gjrGARCH")
```

From the Go-GARCH we can extract the conditional volatilities for each currency as well as the correlation pairs. However, the output for the correlation pairs looks is named in a way that is not very interpretable. As such, I rename them with my renameMGARCH function.

```{r message=FALSE, warning=FALSE}
# Now plotting the volatilities

sigma <- gogarch$Sigma
colnames(sigma) <- colnames(cleaned_fx_xts)
sigma <- sigma %>% 
    xts_tbl() %>% 
    pivot_longer(cols = -date,
                 names_to = "Currency",
                 values_to = "Vol") 
fmxdat::finplot(sigma %>% 
    ggplot() +
    geom_line(aes(x = date,
                  y = Vol,
                  color = Currency)) +
    facet_wrap(~ Currency,
               scales = "free_y")) +
    theme_bw()

# And the correlation pairs
# The output here has super kak naming though so adjust with the following function

pairs <- gogarch$TV_Cor

# The renaming function

pairs <- renameMGARCH(series = cleaned_fx_xts,
                      pairs = pairs,
                      long = T)

fmxdat::finplot(ggplot(pairs %>% dplyr::filter(grepl("SouthAfrica_", Pairs), !grepl("_SouthAfrica", Pairs))) +
    geom_line(aes(x = date,
                  y = Rho,
                  color = Pairs)) +
        facet_wrap(~ Pairs) +
        
    theme_bw() +
    ggtitle("Go-GARCH: SA"))
```
It is difficult to assess which currency is most volatile as they all exhibit similar levels from a visual standpoint. As such, I calculate the mean conditional volatility for each currency. Do this by simply taking the mean of each currencies conditional volatility column.

```{r message=FALSE, warning=FALSE}
# Average vol

sigma %>% 
    group_by(Currency) %>% 
    mutate(Mean_Vol = mean(Vol, na.rm = T)) %>% 
    dplyr::select(-date, -Vol) %>% 
    unique() %>% 
    arrange(desc(Mean_Vol)) %>% 
    gt(caption = "Average Conditional Volatility")
```

From this we see that South Africa is in fact not the most volatile currency in this selection. It is a G10 currency, Japan


