---
author: Joshua-Connor Knapp
title: "Currency Hedging Analysis"
format: pdf
editor: visual
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Necessary packages

rm(list = ls()) 
invisible(gc())
library(pacman)
p_load(rmsfuns, tidyverse, tbl2xts, devtools, PerformanceAnalytics, ggplot2, TTR, RcppRoll, xts, gt, fmxdat, knitr)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Loading the data
# Flooring the date so that it will be the same as the ZAR data to join later

indices <- read_rds("data/Cncy_Hedge_Assets.rds") %>% 
    mutate(date = floor_date(date, "month"))

# Calculating the currency returns

zar <- read_rds("data/Monthly_zar.rds") %>% 
    mutate(fx_change = log(value) - log(lag(value))) %>% 
    dplyr::select(-Tickers) %>% 
    mutate(date = floor_date(date, "month"))
```

The study posits that volatility behaves differently than returns due to the role of covariance in a portfolio. While returns combine linearly, volatility does not. For example, holding two assets with equal returns of 10% and 20% results in an average return of 15%. However, adding a volatile asset to a portfolio doesn’t necessarily increase overall portfolio volatility. This counter intuitive outcome arises from the relationship between assets. If two assets are negatively correlated, their movements can offset each other. For instance, a gain in one asset could neutralize a loss in another, leading to reduced overall volatility. This illustrates how diversification can reduce risk, even when adding a volatile asset, as long as its co-movement with other portfolio assets is favorable.
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Impact of ZAR Hedging", fig1}
# Constructing the global 60 - 40 USD portfolio...

us_hedged_port <- indices %>% 
    dplyr::select(date, MSCI_ACWI, Bbg_Agg) %>% 
    pivot_longer(cols = -date,
                 names_to = "Index",
                 values_to = "Returns") %>% 
    mutate(Weights = ifelse(Index == "MSCI_ACWI", 0.6, 0.4)) %>% 
    group_by(date) %>% 
    mutate(portfolio = sum(Weights * Returns)) %>% 
    dplyr::select(date, portfolio) %>% 
    unique() %>% 
    inner_join(zar, by = "date")

# And recreating the plot from the study

fmxdat::finplot(us_hedged_port %>% 
    ggplot(aes(x = fx_change,
                  y = portfolio))+
    geom_rect(aes(xmin = -Inf, xmax = 0, ymin = 0, ymax = Inf), fill = "yellow4", alpha = 0.002) +  
    geom_rect(aes(xmin = 0, xmax = Inf, ymin = 0, ymax = Inf), fill = "green3", alpha = 0.002) +  
    geom_rect(aes(xmin = -Inf, xmax = 0, ymin = -Inf, ymax = 0), fill = "red", alpha = 0.002) +  
    geom_rect(aes(xmin = 0, xmax = Inf, ymin = -Inf, ymax = 0), fill = "yellow", alpha = 0.002) +  
    geom_point(color = "darkblue",
               alpha = 0.5) +
    geom_smooth(method = "lm",
                color = "darkgrey", 
                se = F) +
    geom_hline(yintercept = 0, 
               color = "black", 
               linetype = "dashed", 
               size = 0.5) +
    geom_vline(xintercept = 0, 
               color = "black", 
               linetype = "dotted", 
               size = 0.5) +
    labs(x = "60-40 Global (USD Returns",
         y = "USD-ZAR Returns"))
```
To illustrate this dynamic, the study estimates a simple 60/40 equity and bond portfolio. In such a portfolio, the rand’s movements can significantly influence overall returns. When global markets perform well, the stronger rand amplifies local returns, while during downturns, a weaker rand cushions global losses in rand terms. This interaction underscores the importance of understanding currency dynamics in portfolios with both local and global components. The scatter plot in Figure 1 above illustrates this relationship, where there is a strong negative correlation between the global portfolio and the rand from December 2004 to January 2022. The study considered a sample period until January 2023, but given data limitations, it was shortened by a year.

This downward slope is explained by the fact that the ZAR does not move in isolation. The same factors influencing the USD influence the ZAR. Positive risk sentiments also tend to favour both. There is also a strong right tail, indicating that the rand experiences deeper monthly depreciations than appreciations. This implies that getting the hedge wrong has a greater cost than getting it right. To further illustrate this, if the simple portfolio now also included local assets with a 70% local and 30% global split and rebalanced quarterly, consider the outcomes of a hedged and unhedged alternative represented in Table 1 below. A hedged portfolio does not account for rand exosure, while an unhedged portfolio does. 
```{r echo=FALSE, message=FALSE, warning=FALSE, tab.cap="Portfolio Performance"}
# Here we want to estimate the portfolios
# Estimate the weights of the index according to specifications

weights <- data.frame(Index = colnames(indices)[sapply(indices, is.numeric)],
                      Weights = c(0.6 * 0.3, 0.4 * 0.3, 0.6 * 0.7, 0.4 * 0.7))

# Estimating an hedged index
# Hedged indices are those that do not account for rand exposure, so we do nothing to these indices

hedged_indices <- indices 

hedged_port <- estimatePORT(data = hedged_indices,
                            size = 1000,
                            months = c(3, 6, 9, 12),
                            weights = weights)

# Now estimating as un-hedged portfolio
# Need to control USD returns for currency effects, do this by adding the change in the rand to the USD indices

unhedged_indices <- indices %>% 
    inner_join(zar, by = "date") %>% 
    mutate(MSCI_ACWI = MSCI_ACWI + fx_change,
           Bbg_Agg = Bbg_Agg + fx_change) %>%
    dplyr::select(-fx_change, -value) 

unhedged_port <- estimatePORT(data = unhedged_indices,
                              size = 1000,
                              months = c(3, 6, 9, 12),
                              weights = weights)

# Annualized returns
# The USD portfolio

us_hedged_annual_ret <- us_hedged_port %>% 
    dplyr::select(date, portfolio) %>% 
    tbl_xts() %>% 
    Return.annualized(R = ., 
                      scale = 12) %>% 
    data.frame()

# The local global hedged portfolio

hedged_annual_ret <- hedged_port$returns %>% 
    xts_tbl() %>% 
    filter(date >= ymd(20041201) & date <= ymd(20221201)) %>% 
    tbl_xts() %>% 
    Return.annualized(R = ., 
                      scale = 12) %>% 
    data.frame()

# The local global unhedged portfolio

unhedged_annual_ret <- unhedged_port$returns %>% 
    xts_tbl() %>% 
    filter(date >= ymd(20041201) & date <= ymd(20221201)) %>% 
    tbl_xts() %>% 
    Return.annualized(R = ., 
                      scale = 12) %>% 
    data.frame()

# Annualized SD
# The USD portfolio

hedged_annual_sd <- hedged_port$returns %>% 
    sd.annualized(x = ., 
                      scale = 12)

# The local global hedged portfolio

unhedged_annual_sd <- unhedged_port$returns %>% 
    sd.annualized(x = ., 
                      scale = 12)

# The local global unhedged portfolio

us_hedged_annual_sd <- us_hedged_port %>% 
    dplyr::select(date, portfolio) %>% 
    filter(date >= ymd(20041201) & date <= ymd(20221201)) %>% 
    tbl_xts() %>% 
    sd.annualized(x = ., 
                  scale = 12)

# Putting all into a table

port_comp_table <- data.frame(Fund = c("Global (USD Returns: Hedged","Global + Local (Hedged)", "Global + Local (Unhedged"),
                        "Returns Ann." = c(us_hedged_annual_ret$portfolio, hedged_annual_ret$portfolio.returns, unhedged_annual_ret$portfolio.returns),
                        "Std Ann." = c(us_hedged_annual_sd, hedged_annual_sd, unhedged_annual_sd))

port_comp_table %>% 
    kable(caption = "Portfolio Performance")
```
We can see here that the unhedged fund has greater annualised returns and lower annualized volatility. These results are not an exact replication of the study, but they are very similar and echoe the same sentiments. Delving even deeper, downside risk estimates represented in Table 2 indicate that the hedged fund has a greater maximum drawdown, value at risk, and expected shortfall. 
```{r echo=FALSE, message=FALSE, warning=FALSE, tab.cap="Downside Risk Estimates"}
# Looking at downside risks

portfolios <- left_join(hedged_port$returns %>% xts_tbl() %>% rename("Hedged" = portfolio.returns),
                            unhedged_port$returns %>% xts_tbl() %>% rename("Unhedged" = portfolio.returns),
                            by = "date") %>% 
    filter(date >= ymd(20041201) & date <= ymd(20221201)) %>% 
    tbl_xts()
    
downside_table <- PerformanceAnalytics::table.DownsideRisk(R = portfolios,
                                             ci = 0.95,
                                             Rf = 0, 
                                             MAR = 0) %>% data.frame() %>% 
    rownames_to_column(var = "Estimate") 

downside_table[c(1,5,7,8:11),] %>% 
    kable(caption = "Downside Risks")
    
```
The plots that follow visualize the arguments made here. The unhedged portfolio sees much higher cumulative returns and sees a lower rolling 12-month volatility (I know the 12-month vol is not annualized)
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Rolling 12-Month Standard Deviation", fig.height=3}

chart.RollingPerformance(R = portfolios,
                         FUN = "sd",
                         main = "",
                         width = 12,
                         legend.loc = "bottomleft",
                         colorset = c("steelblue", "orange"))
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Cumulative Returns", fig.height=3}
chart.CumReturns(R = portfolios,
                 width = 12, 
                 main = "",
                 legend.loc = "topleft",
                 colorset = c("steelblue", "orange"))
```


